Factoring with $n+2$ clean qubits and $n-1$ dirty qubits

### 2017-06-02 doc/paper.tex
Typo fix
that optimizations will preserve the behavior

We do not attempt to define or implement reasonable behavior for modular arithmetic circuits applied to out of range values (ones equal to or larger than the modulus).
This {\em includes input values}.
For example, if our modular addition construction ($x \mathrel{{+}{=}} y \pmod{R}$) is applied to a $y \geq R$, then we don't guarantee that $y \mod R$ will be added into $x$ or that the operation will commute with other additions or that anything sensible at all will happen.
If the precondition $y < R$ is violated, what occurs is undefined behavior \cite{c11}.

@@

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{assets/inline-adder.png}
  \caption{ Adder for input and target registers of the same size.
  Requires no ancillae, and uses $O(N)$ gates and depth.
  Based on \cite{van2004, takahashi2005}.}
  \label{fig:inlineadder}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{assets/increment-many-dirty.png}
  \caption{ Subtracting $x$ and $-x-1$ from a register increments it. Requires $O(n)$ depth, size, and $n$ dirty ancillae.}
  \label{fig:increment-many-dirty}
\end{figure}

>>>>

We do not attempt to define or implement reasonable behavior for modular arithmetic circuits applied to out of range values (ones equal to or larger than the modulus).
This {\em includes input values}.
For example, if our modular addition construction ($x \mathrel{{+}{=}} y \pmod{R}$) is applied to a $y \geq R$, then we don't guarantee that $y \mod R$ will be added into $x$, that the operation will commute with other additions, that optimizations won't change the behavior, or that anything sensible at all will happen.
If the precondition $y < R$ is violated, what occurs is undefined behavior \cite{c11}.

@@

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{assets/inline-adder.png}
  \caption{ Adder for input and target registers of the same size.
  Requires no ancillae, and uses $O(n)$ gates and depth.
  Based on \cite{van2004, takahashi2005}.}
  \label{fig:inlineadder}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=\linewidth]{assets/increment-many-dirty.png}
  \caption{ Subtracting $x$ and $-x-1$ from a register increments it. Requires $O(n)$ depth and size, and $n$ dirty ancillae.}
  \label{fig:increment-many-dirty}
\end{figure}
